Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-04-22 paper.qmd
Add corbett paper

---
title: "Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
format: pdf
number-sections: true
bibliography: references.bib
editor:
  markdown: 
    wrap: sentence
---

@@

As shown in @sec-methods.

test test [@prati2019].

>>>>

---
title: "Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
format: pdf
number-sections: true
bibliography: references.bib
editor:
  markdown: 
    wrap: sentence
# knitr:
#   opts_chunk:
#     fig.path: images/
# # # Uncomment for formatted version
  # elsevier-pdf:
  #   linestretch: 2
  #   keep-tex: true
  #   journal:
  #     name: European Transport Research Review
  #     formatting: preprint
  #     model: 3p
  #     cite-style: super
# # # #   # pdf: default

# # Uncomment the following line to produce the cover page
author:
  - name: Graham Farrell
    affiliations:
      - name: University of Leeds
        address: TBC
        orcid: TBC
  - name: Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
        orcid: 0000-0001-5679-6536
  - name: Steve O'Hern
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
        orcid: tbc
keywords: 
  - Cycling
  - Hotspots 
  - Road Safety
  - Active Travel
  - Transport Planning
  - Near Misses
date: last-modified
---

@@

Dangerous and criminal driving are significant problems that take many forms [@simon1996] [@corbett2010; @corbett2003] (Corbett 2003, 2010).
Across Great Britain there were an estimated 1,711 fatalities resulting from a road traffic crash in 2022 and 135,480 causalities reported across all severities (ref).
Most injuries involve motor vehicle occupants, however when accounting for the distance travelled by road user groups, cyclists are over-represented in injury statistics (ref).
